---
title: "Corrected R file 10/01/2022"
author: "Oussama, Julie, Victória"
date: "2023-01-10"
output:
    html_document:
    code_folding: hide           
    highlight: tango             
    toc: yes                    
    toc_depth: 6 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("readxl", dependencies = TRUE)
# install.packages("ggplot2", dependencies = TRUE)
# install.packages(c("ggplot2", "ggpubr", "tidyverse", "broom", "AICcmodavg"), , dependencies = TRUE)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(ggplot2)
```
#### This file is regarding the results for the water stress green house experiment - Group 5

## Chapter 1 - Downloading the data
The initial step is the aggregation of all data from the groups (1-5) in a shared Excel file on Google Drive. This document should be downloaded as an excel sheet named "Data", in this project's repository folder. 

* add chunk for downloading data 
```{r}

```

In order to import this data we used the package "readxl".
```{r}
readxl::read_excel("data_dec/water_stress.xlsx")
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
```
After importing the data, we give it the name of d0. Next step is to visualize it, by creating different plots.

## Chapter 2 - Visualization of data with plots. 
In this step we want to create many plots in order to better visualize the data.
We will use X= Date and Y= Variable (Y1= Plant height ; Y2= Leaf number ; Y3= Leaf lenght ; Y4= Leaf width ; Y5= Leaf area ; Y7= Chlorophyll ) 

##### First plot with all species
```{r, fig.height=15}
ggplot(d0, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()+
  facet_grid(Species ~.)
```

This next code chunk is meant to help visualize only one species (Solanum lycopersicum) and script on how to plot it
```{r}
# For Solanum lycopersicum
s1 <- d0[d0$Species=="Solanum lycopersicum",]
ggplot(s1, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()
```

Now we create a for loop to visualize all the species and all the variables 
```{r, eval=TRUE}
v1 <- c("Plant_height", "Leaf_width", "Leaf_length", "Leaf_area", "Leaf_number", "Root_length", "Chlorophyll_content", "Soil_humidity", "Electrical_conductivity")
i <- "Beta vulgaris"
variable <- "Plant_height"

for(i in levels(as.factor(d0$Species))) {
  for(variable in v1) {
    s1 <- d0[d0$Species==i, c(variable, "Week", "PlantId", "Treatment")]
    s1 <- na.exclude(s1)
    p <- ggplot(s1, aes(x= Week, y= .data[[variable]], group= PlantId, color= Treatment)) + 
      geom_line() + 
      labs(title = i)
    print(p)
  }
}

```

## Chapter 3 - ANOVA
For the third part of this project, we will advance with statistical calculations. For this we used multiple packages including ggplot2", "ggpubr", "tidyverse", "broom" and "AICcmodavg". Now that we have seen all the variables and the difference for species over time, we can choose which week is better for demonstrating each one of them based on which week shows the most change.  

##### Plant Height
For the plant height variable the most visual difference is present in week 6 (w6)
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Plant_height") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Plant_height ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y= Plant_height, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf number 
For the leaf number variable we have chosen the weeks XX  because ??
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_number") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_number ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_number, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_number") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_number ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_number, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf length
For the leaf length variable we have chosen the weeks XX  because ??
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_length ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_length ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf width
For the leaf width variable we have chosen the weeks XX  because ??
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_width") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_width ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_width, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_width") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_width ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_width, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf area
For the leaf area variable we have chosen the weeks XX  because ??
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_area") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_area ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_area, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_area") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_area ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_area, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Chlorophyll content
For the leaf chlorophyll content variable we have chosen the weeks XX  because ??
###### Week 3
```{r, fig.width=10}
d1 <- d0[d0$Week == "W3" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
###### Week 4
```{r, fig.width=10}
d1 <- d0[d0$Week == "W4" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
###### Week 5
```{r, fig.width=10}
d1 <- d0[d0$Week == "W5" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Aerial fresh weight 
For the aerial fresh weight variable, the data was is just present in week 6 since it required the depotting of the plant samples.
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_fresh_weight") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Aerial_fresh_weight ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Aerial_fresh_weight, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

##### Aerial dry weight 
For the aerial dry weight variable, the data was is just present in week 6 since it required the depotting of the plant samples and the drying of the fresh weight.
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_dry_weight") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Aerial_dry_weight ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Aerial_dry_weight, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

##### Root length
For the root lenght variable, the data was is just present and measure for week 6.
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Root_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Root_length ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Root_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

## Chapter 4 - PCA analysis
In this chapter we move foward with the statistical analysis by doing a PCA analysis for the data.


To start, we need to make a subset for the data with only numerical variables and exclude the other variables, scale the data and after that we will exclude all the missing data
```{r}
PCA_data <- d0[c(8:9, 11:21)]
PCA_data_scaled <- as.data.frame(scale(PCA_data))
view(PCA_data_scaled)

# exclude missing values NA

PCA_data01 <- na.exclude(PCA_data_scaled)

```

 now we are going to do a PCA of the data
 
```{r}
PCA <- prcomp(PCA_data01, scale = FALSE)
print(PCA)
```
 
now we will plot the PCA results
```{r}
# Plotting the PCA results
# install.packages("factoextra") 
#if(!require(devtools)) install.packages("devtools")
#devtools::install_github("kassambara/factoextra")  

library(factoextra)
library(ggplot2)

fviz_eig(PCA)

# graph for individuals



fviz_pca_ind(PCA,
             col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
)



# graph of variable


fviz_pca_var(PCA,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
)


```

