---
title: "final R markdown 10_01_2023"
author: "oussama, julie, vectoria"
date: '`r Sys.Date()`'
output: 
    html_document:
    code_folding: hide           
    highlight: tango             
    toc: yes                    
    toc_depth: 6 
---

```{r setup, include=FALSE}
if (!dir.exists("results")) dir.create("results")  # create folder if necessary
knitr::opts_chunk$set(              # nice results format
  fig.path = "results22/",            # Folder for figures
  dev = "png",                      # png format for figures
  dev.args = list(type = "cairo"),  # png args. Improves png
  dpi = 100                         # 100 for working, 300 for publication
)
# install.packages("readxl", dependencies = TRUE)
# install.packages("ggplot2", dependencies = TRUE)
# install.packages(c("ggplot2", "ggpubr", "tidyverse", "broom", "AICcmodavg"), , dependencies = TRUE)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(ggplot2)
library(agricolae)
```

#### This file is regarding the results for the water stress green house experiment - Group 5

## Chapter 1 - Downloading the data
> The initial step is the aggregation of all data from the groups (1-5) in a shared Excel file on Google Drive. This document should be downloaded as an excel sheet named "Data", in this project's repository folder. In order to import this data we used the package "readxl".

```{r}
readxl::read_excel("data_dec/water_stress.xlsx")
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
```

> After importing the data, we give it the name of d0. Next step is to visualize it, by creating different plots.

## Chapter 2 - Visualization of data with plots. 
>In this step we want to create many plots in order to better visualize the data.
We will use X= Date and Y= Variable (Y1= Plant height ; Y2= Leaf number ; Y3= Leaf lenght ; Y4= Leaf width ; Y5= Leaf area ; Y7= Chlorophyll )

**the code used for this step is : 
ggplot(d0, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()+
  facet_grid(Species ~.)**
  
  
##findings
  > after seeing all the charts, we selected the ones below because:
  
  > *  we want to make the R markdown file visually appealing by avoiding plotting all variables for all species.
  
  > *  we consider the graphs below representative of the general trends observed in the other species and variables.
  
  > *  we have chosen to analyze the data for week 6, because the effect of the water stress deficit is clearer for this week. 
  
  
> This next code chunk is meant to help visualize only soil humidity for two species (Solanum lycopersicum and lolium perenne) and script on how to plot it

```{r}
# For Solanum lycopersicum

s1 <- d0[d0$Species=="Solanum lycopersicum",]
ggplot(s1, aes(x= Week, y= Soil_humidity, group= PlantId, color= Treatment)) + 
  geom_line()
  
# For 	Lolium perenne
s2 <- d0[d0$Species=="Lolium perenne",]
ggplot(s2, aes(x= Week, y= Soil_humidity, group= PlantId, color= Treatment)) + 
  geom_line() 
```


> This next code chunk is meant to help visualize only the variable "Plant_height" for the species (Raphanus sativus) and script on how to plot it 

```{r}
# For 	Raphanus sativus

s3 <- d0[d0$Species=="Raphanus sativus",]
ggplot(s3, aes(x= Week, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()
```

# Chapter 3 - ANOVA

> For the third part of this project, we will advance with statistical calculations. For this we used multiple packages including ggplot2", "ggpubr", "tidyverse", "broom" and "AICcmodavg". Now that we have seen all the variables and the difference for species over time, as we said before we have chosen  the week 6 to do the analyses.

## Linear model 


### Soil_humidity


```{r, fig.width=10}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Soil_humidity") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Soil_humidity ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Soil_humidity~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Soil_humidity, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y =max(d1$Soil_humidity) , label = Letters))+
   theme_pubclean()+
  labs(title = 'Figure 01. The effect of water deficit treatments on the soil humidity (%) of the different species.')
```








### Plant_height

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}

#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Plant_height") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Plant_height ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

# the objective here is create a table using a for loop function, and fill it with the results of Tukey HSD (letters), and automatically assign these letters to the box plots for each species. 

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Plant_height~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Plant_height, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y =max(d1$Plant_height) , label = Letters))+
   theme_pubclean()+
  labs(title = 'Figure 02. The effect of water deficit on the plant height (cm) of the different species.')         

```








### Leaf_number

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_number") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Leaf_number ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Leaf_number~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Leaf_number, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Leaf_number), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 03. The effect of water deficit on the leaf number of the different species.')

```









### Leaf_length

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_length") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Leaf_length ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Leaf_length~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Leaf_length, fill= Species)) + 
  geom_boxplot(how.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Leaf_length), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 04. The effect of water deficit  on the leaf lenght (cm) of the different species.')
```








### Leaf_width

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_width") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Leaf_width ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Leaf_width~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Leaf_width, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Leaf_width), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 05. The effect of water deficit  on the leaf width (cm) of the different species.')
```










### Leaf_area

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}

#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_area") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Leaf_area ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Leaf_area~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Leaf_area, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Leaf_area), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 06. The effect of water deficit  on the leaf area (%) of the different species.')
```








### Chlorophyll_content

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}

# #performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Chlorophyll_content") ]

d1 <- na.exclude(d1)
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)

# Performing  Tukey HSD analysis
 
rl <- length(levels(as.factor(d1$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d1$Species))) {


d2 <- d1[d1$Species == i,]

model <- aov(Chlorophyll_content~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3
}


# plotting the ANOVA results
 
ggplot(d1, aes(x= Treatment, y= Chlorophyll_content, fill= Species)) +
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Chlorophyll_content), label = Letters))+ 
  theme_pubclean()+
   labs(title = 'Figure 07. The effect of water deficit  on the chlorophyll content (SPAD Unit) of the different species.')
```








### Aerial_fresh_weight

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_fresh_weight") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Aerial_fresh_weight ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Aerial_fresh_weight~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Aerial_fresh_weight, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Aerial_fresh_weight), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 07. The effect of water deficit  on the aerial fresh weight (g) of the different species.')

```









### Aerial_dry_weight

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_dry_weight") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Aerial_dry_weight ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Aerial_dry_weight~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Aerial_dry_weight, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Aerial_dry_weight), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 08. The effect of water deficit  on the aerial dry weight (cm) of the different species.')

```







### Root_length

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
 
# performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Root_length") ]
d1 <- na.exclude(d1)
lm1 <- lm(Root_length ~ Treatment + Species, data=d1)
anova(lm1)

 
# Performing  Tukey HSD analysis
 
rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {


d2 <- d1[d1$Species == i,]

model <- aov(Root_length~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3
}


# # plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Root_length, fill= Species)) +
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Root_length), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 09. The effect of water deficit  on the root lenght (cm) of the different species.')

  
```










### Roots_fresh_weight

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Roots_fresh_weight") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Roots_fresh_weight ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Roots_fresh_weight~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Roots_fresh_weight, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Roots_fresh_weight), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 10. The effect of water deficit  on the root fresh weight (g) of the different species.')
```








### Roots_dry_weight

```{r, fig.width=10, echo=FALSE, results = FALSE, message=FALSE, warning=FALSE}
#performing the ANOVA analysis

d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Roots_dry_weight") ]
d1 <- na.exclude(d1) 
lm1 <- lm(Roots_dry_weight ~ Treatment + Species, data=d1)
anova(lm1)


# Performing  Tukey HSD analysis

rl <- length(levels(as.factor(d0$Species)))*3  #number of rows

df0 <- data.frame(Treatment = character(), Species = character(), Letters = character())
df0[1:rl,] <- NA
k = 1
i <- levels(as.factor(d0$Species))[1]
for (i in levels(as.factor(d0$Species))) {
  

d2 <- d1[d1$Species == i,]

model <- aov(Roots_dry_weight~Treatment, data =d2 )

hsd <- HSD.test(model, "Treatment")

df0$Treatment[k:(k+2)] <- row.names(hsd$groups)
df0$Species [k:(k+2)] <- i
df0$Letters [k:(k+2)] <- hsd$groups$groups

k <- k+3  
}


# plotting the ANOVA results

ggplot(d1, aes(x= Treatment, y= Roots_dry_weight, fill= Species)) + 
  geom_boxplot(show.legend = FALSE) +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0)) +
  geom_text(data =df0 , aes(y = max(d1$Roots_dry_weight), label = Letters))+
  theme_pubclean()+
  labs(title = 'Figure 11. The effect of water deficit  on the root dry weight (g) of the different species.')
```










## PCA analysis:
> in this part we are going to do a PCA analysis for the data.
Next we need to make a subset for the data with only numerical variables and exclude the other variables, scale the data and after that we will exclude all the missing data.

 
>now we will plot the PCA results
```{r}

d5 <- d0[d0$Week == "W6", c(4,7, 8, 11:21)]
d6 <- na.exclude(d5)

data2 <- d0[d0$Week == "W6", c(8, 11:21)]
data3 <- na.exclude(data2)

PCA_data_scaled1 <- as.data.frame(scale(data3))

PCA <- prcomp(PCA_data_scaled1, scale = FALSE)
library(factoextra)
library(ggplot2)

fviz_eig(PCA)

# graph for individuals

fviz_pca_biplot(PCA,
             col.ind = d6$Species,
             label = "var",
             addEllipses = TRUE,
             repel = TRUE     # Avoid text overlapping 
             
) + 
   scale_shape_manual(values=rep(19,7))

```


