---
title: "Preliminary results"
author: "Julie, Oussama and Victória "
date: "2022-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This file is regarding the preliminary results for the water stress green house experiment - Group 5
# Chapter 1 - First dealing with data
##### Visualization of data with plots.
```{r}
# install.packages("readxl")
readxl::read_excel("data_dec/water_stress.xlsx")
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
```
Visualization of data with plots. 
Create many plots.

X= Date 
Y= Variable 
Y1= Plant height 
Y2= Leaf number 
Y3= Leaf lenght 
Y4= Leaf width 
Y5= Leaf area 
Y7= Chlorophyll 

S1 : Solanum lycopersicum
```{r, fig.height=15}
# install.packages("ggplot2", dependencies = TRUE)
library(ggplot2)

# All species
ggplot(d0, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()+
  facet_grid(Species ~.)

```
```{r}
# For Solanum lycopersicum
s1 <- d0[d0$Species=="Solanum lycopersicum",]
ggplot(s1, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()

```


S2 : Amaranthus retroflexus
```{r}


```


S3 : Spinacia oleracea
```{r}

```


S4 : Amaranthus retroflexus
```{r}

```


S5 : Hordeum vulgare
```{r}

```


S6 : Lolium perenne
```{r}

```


S7 : Beta vulgaris
```{r}

```


S8 : Sonchus oleraceus
```{r}

```


S9 : Portulacea oleracea
```{r}

```


S10 : Raphanus sativus
```{r}

```

# Chapter 2 - ANOVA

```{r}
#Packages
#install.packages(c("ggplot2", "ggpubr", "tidyverse", "broom", "AICcmodavg"), , dependencies = TRUE)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)

#Import data
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
d0
names(d0)
```


##### Linear model 
##### Plant Height 
Most visual difference is in week 6 (w6)
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Plant_height") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Plant_height ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y= Plant_height, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf number 
Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_number") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_number ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_number, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_number") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_number ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_number, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf length
Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_length ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_length ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf width
Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_width") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_width ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_width, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_width") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_width ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_width, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf area
Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_area") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_area ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_area, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_area") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_area ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_area, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Chlorophyll content
Week 3
```{r, fig.width=10}
d1 <- d0[d0$Week == "W3" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
Week 4
```{r, fig.width=10}
d1 <- d0[d0$Week == "W4" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
Week 5
```{r, fig.width=10}
d1 <- d0[d0$Week == "W5" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Aerial fresh weight 
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_fresh_weight") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Aerial_fresh_weight ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Aerial_fresh_weight, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

##### Aerial dry weight 
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_dry_weight") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Aerial_dry_weight ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Aerial_dry_weight, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

##### Root length
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Root_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Root_length ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Root_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

