---
title: "First"
author: "Julie, Oussama and Victória "
date: "2022-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First dealing with data
```{r}
# install.packages("readxl")
readxl::read_excel("data_dec/water_stress.xlsx")
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
```


Visualization of data with plots. 
Create many plots.

#### One plot for each species with variables and treatments (control, intermediate, waterstress)
X= Date 
Y= Variable 
Y1= Plant height 
Y2= Leaf number 
Y3= Leaf lenght 
Y4= Leaf width 
Y5= Leaf area 
Y7= Chlorophyll 

S1 : Solanum lycopersicum
```{r, fig.height=15}
# library(ggplot2)
# All species
ggplot(d0, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()+
  facet_grid( Species ~. )

# For Solanum lycopersicum
s1 <- d0[d0$Species=="Solanum lycopersicum",]
ggplot(d1, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()

```


S2 : Amaranthus retroflexus
```{r}

```


S3 : Spinacia oleracea
```{r}

```


S4 : Amaranthus retroflexus
```{r}

```


S5 : Hordeum vulgare
```{r}

```


S6 : Lolium perenne
```{r}

```


S7 : Beta vulgaris
```{r}

```


S8 : Sonchus oleraceus
```{r}

```


S9 : Portulacea oleracea
```{r}

```


S10 : Raphanus sativus
```{r}

```

#### Plot for 