---
title: "Preliminary results group 5 21/12/2022"
author: "oussama, julie, vectoria"
date: "2022-12-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This file is regarding the preliminary results for the water stress green house experiment - Group 5

# Chapter 1 - First dealing with data
##### Visualization of data with plots.
```{r}

# first thing to do is importing the data
# install.packages("readxl")
readxl::read_excel("data_dec/water_stress.xlsx")
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
```

after importing the data and give it the name of d0, we are going to visualize it, by creation different plots.


##Visualization of data with plots. 
Create many plots.

X= Date 
Y= Variable 
Y1= Plant height 
Y2= Leaf number 
Y3= Leaf lenght 
Y4= Leaf width 
Y5= Leaf area 
Y7= Chlorophyll 


```{r, fig.height=15}
# install.packages("ggplot2", dependencies = TRUE)
library(ggplot2)

# first we are going to visualize all the species in a plot
ggplot(d0, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()+
  facet_grid(Species ~.)

```



in this code chunk we are try to visualize one species, to know how to plot it first
```{r}
# For Solanum lycopersicum
s1 <- d0[d0$Species=="Solanum lycopersicum",]
ggplot(s1, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()
```

then we will create a for loop to visualize all the species and all the variables 

```{r, eval=TRUE}
v1 <- c("Plant_height", "Leaf_width", "Leaf_length", "Leaf_area", "Leaf_number", "Root_length", "Chlorophyll_content", "Soil_humidity", "Electrical_conductivity")
i <- "Beta vulgaris"
variable <- "Plant_height"

for(i in levels(as.factor(d0$Species))) {
  for(variable in v1) {
    s1 <- d0[d0$Species==i, c(variable, "Week", "PlantId", "Treatment")]
    s1 <- na.exclude(s1)
    p <- ggplot(s1, aes(x= Week, y= .data[[variable]], group= PlantId, color= Treatment)) + 
      geom_line() + 
      labs(title = i)
    print(p)
  }
}

```

```

## Chapter 2 - ANOVA
in this part we are trying to do an ANOVA analysis for the data

```{r}
#Packages
#install.packages(c("ggplot2", "ggpubr", "tidyverse", "broom", "AICcmodavg"), , dependencies = TRUE)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)

#Import data
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
d0
names(d0)
```


##### Linear model 
##### Plant Height 
Most visual difference is in week 6 (w6)
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Plant_height") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Plant_height ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y= Plant_height, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf number 
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_number") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_number ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_number, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_number") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_number ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_number, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf length
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_length ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_length ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y= Leaf_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf width
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_width") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_width ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_width, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_width") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_width ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_width, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Leaf area
###### Week 1
```{r, fig.width=10}
d1 <- d0[d0$Week == "W1" , c("Treatment", "Species", "Leaf_area") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_area ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_area, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Leaf_area") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Leaf_area ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Leaf_area, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Chlorophyll content
###### Week 3
```{r, fig.width=10}
d1 <- d0[d0$Week == "W3" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
###### Week 4
```{r, fig.width=10}
d1 <- d0[d0$Week == "W4" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
###### Week 5
```{r, fig.width=10}
d1 <- d0[d0$Week == "W5" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```
###### Week 6
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Chlorophyll_content") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Chlorophyll_content ~ Treatment + Species, data=d1)
anova(lm1)
ggplot(d1, aes(x= Treatment, y=Chlorophyll_content, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))
```

##### Aerial fresh weight 
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_fresh_weight") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Aerial_fresh_weight ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Aerial_fresh_weight, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

##### Aerial dry weight 
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Aerial_dry_weight") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Aerial_dry_weight ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Aerial_dry_weight, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```

##### Root length
```{r, fig.width=10}
d1 <- d0[d0$Week == "W6" , c("Treatment", "Species", "Root_length") ]
d1 <- na.exclude(d1) #remove the ones with empty cells 
lm1 <- lm(Root_length ~ Treatment + Species, data=d1)
anova(lm1)
summary(lm1)
ggplot(d1, aes(x= Treatment, y=Root_length, fill= Species)) + 
  geom_boxplot() +
  facet_grid(. ~ Species) +
  theme(strip.text.x = element_text(size=0))

```


## part3: PCA analysis
in this part we are going to do a PCA analysis for the data

```{r}

#importing data

#we already imported the data in the previous parts, that's why the functions of importing the data are commented

#readxl::read_excel("data_dec/water_stress.xlsx")
#d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
```

Next we need to make a subset for the data with only numerical variables and exclude the other variables, scale the data and after that we will exclude all the missing data
```{r}
PCA_data <- d0[c(8:9, 11:21)]
PCA_data_scaled <- as.data.frame(scale(PCA_data))
view(PCA_data_scaled)

# exclude missing values NA

PCA_data01 <- na.exclude(PCA_data_scaled)

```

 now we are going to do a PCA of the data
 
```{r}
PCA <- prcomp(PCA_data01, scale = FALSE)
print(PCA)
```
 
now we will plot the PCA results
```{r}
# Plotting the PCA results
# install.packages("factoextra") 
#if(!require(devtools)) install.packages("devtools")
#devtools::install_github("kassambara/factoextra")  

library(factoextra)
library(ggplot2)

fviz_eig(PCA)

# graph for individuals



fviz_pca_ind(PCA,
             col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
)



# graph of variable


fviz_pca_var(PCA,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
)


```

