---
title: "First"
author: "Julie, Oussama and Victória "
date: "2022-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First dealing with data
```{r}
# install.packages("readxl")
readxl::read_excel("data_dec/water_stress.xlsx")
d0 <- readxl::read_excel("data_dec/water_stress.xlsx", sheet = "Data")
```


Visualization of data with plots. 
Create many plots.

#### One plot for each species with variables and treatments (control, intermediate, waterstress)
X= Date 
Y= Variable 
Y1= Plant height 
Y2= Leaf number 
Y3= Leaf lenght 
Y4= Leaf width 
Y5= Leaf area 
Y7= Chlorophyll 

```{r}

```


S1 : Solanum lycopersicum
```{r, fig.height=15}
#install.packages("ggplot2", dependencies = TRUE)
library(ggplot2)

# All species
ggplot(d0, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()+
  facet_grid( Species ~. )

# For Solanum lycopersicum
s1 <- d0[d0$Species=="Solanum lycopersicum",]
ggplot(s1, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
  geom_line()

#For loop = for all the species

#essai1
v1 <- c("Plant_height", "Chlorophyll_content" ,"Roots_dry_weight")

for(i in levels(as.factor(d0$Species))) {
  for(variable in v1) {
    s1 <- d0[d0$Species==i,]
    ggplot(s1, aes(x= Week, y= s1[ ,v1], group= PlantId, color= Treatment)) + 
      geom_line()
  }
}

#essai2
for(i in levels(d0$Species)) {
  for(variable in 1:10) {
    s2 <- d0[d0$Species,]
    ggplot(s2, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment)) + 
      geom_line()
  }
}

#essai3
for(i in levels(d0$Species)){
  tf <- d0$Species=="Solanum lycopersicum"
  ggplot(tf, aes(x = Date, y= Plant_height, group= PlantId, color= Treatment)) + 
      geom_line()
}

#essai4
for(i in 2:ncol(d0)) {                      
  print(ggplot(d0, aes(x= Date, y= Plant_height, group= PlantId, color= Treatment, data[ , i])) +
          geom_line())
  Sys.sleep(2)
}
```

S2 : Amaranthus retroflexus
```{r, fig.height=15}
 

```


S3 : Spinacia oleracea
```{r}

```


S4 : Amaranthus retroflexus
```{r}

```


S5 : Hordeum vulgare
```{r}

```


S6 : Lolium perenne
```{r}

```


S7 : Beta vulgaris
```{r}

```


S8 : Sonchus oleraceus
```{r}

```


S9 : Portulacea oleracea
```{r}

```


S10 : Raphanus sativus
```{r}

```

#### Plot for 